---
title: "Guia de estudio Metodos Estadísticos"
author: "Carol Otero"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: book.bib
description: |
  Esta es una recopilación de los apuntes del Diplomado de Estadística, énfasis en métodos estadísticos con R y adicional con Python.
link-citations: true
github-repo: "rstudio/bookdown-demo"
---

# Introduccion

Aqui empieza todo, el objetivo es plasmar los apuntes del diplomado y como se ejecuta el script en r y en python para solucionar preguntas estadisticas. Nuevo cambio. Otro cambio.

# Cross-references {#cross}

Cross-references make it easier for your readers to find and link to elements in your book.

## Chapters and sub-chapters

There are two steps to cross-reference any heading:

1.  Label the heading: `# Hello world {#nice-label}`.
    -   Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    -   To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.
2.  Next, reference the labeled heading anywhere in the text using `\@ref(nice-label)`; for example, please see Chapter \@ref(cross).
    -   If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#cross).

## Captioned figures and tables

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig-2).

```{r nice-fig-2, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab-2).

```{r nice-tab-2, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
